---
title: "Momentum Index"
output: 
  html_document:
    keep_md: TRUE
---
```{r,echo=FALSE,message=FALSE,warning=FALSE}
require(lubridate)
```

`r today()`

Some charts for historical value of "Momentum Index", defined as 6 month return divided by annual volatility measured on trailing 6 months data.  

We plot the momentum index and add dotted lines for quartiles.  As you would expect, the quartiles are not symmetric around zero for assets with a positive expected return.

We then plot the momentum index against the next three month return.  Quartiles are shown again as dotted lines (now vertical).  The green line is an OLS regression. A vertical red line is the current value of the momentum index with two red dots for a one-sigma confidence interval.   Finally, we show regression statistics. 


```{r,echo=TRUE,message=FALSE,warning=FALSE}
require("Rbbg")
require("lubridate")
require("zoo")
conn=blpConnect(verbose=FALSE)
tickers=c("SPX Index","MID Index","SML Index","MXEA Index",
         "MSDLEAFE Index","MXEASC Index","NCLDEAFE Index","MXEF Index","NDLEEGF Index",
         "BCOM Index","CL1 Comdty","XB1 Comdty","C 1 Comdty","HG1 Comdty","XAU Curncy",
         "EURUSD Curncy","GBPUSD Curncy","JPYUSD Curncy")
names(tickers)=c("S&P 500","Mid Cap","Small Cap","EAFE",
                "EAFE Local","EAFE Small","EAFE Small Local","Emg Mkts","Emg Mkts Local",
                "Commodities","WTI","Gasoline","Corn","Copper","Gold",
                "Euro/USD","GBP/USD","Yen/USD")
# tickers=c("AAPL US EQUITY","AMZN US EQUITy","MSFT US EQUITY")
# names(tickers)=c("Apple","Amazon","Microsoft")
flds=c("PX_LAST","VOLATILITY_180D")
for (j in 1:length(tickers)) {
  ticker=tickers[j]
  tname=names(tickers)[j]
  dat=bdh(conn,ticker,flds,Sys.Date()-(366*30),
          option_names="periodicitySelection",option_values="MONTHLY")
  dat2=bdh(conn,ticker,flds,Sys.Date()-183)
  excl=which(apply(is.na(dat2),1,any))
  if(length(excl)>0) dat2=dat2[-excl,]
  pxz=zoo(dat$PX_LAST,as.Date(dat$date))
  volz=zoo(dat$VOLATILITY_180D,as.Date(dat$date))
  lastvol=dat2$VOLATILITY_180D[dim(dat2)[1]]
  volz=c(volz,zoo(lastvol,today()+1))
  rho=diff(log(pxz))
  rhof3=rollapply(rho,FUN=sum,align='left',width=3)
  rhof3=100*(-1+exp(rhof3))
  rhot6=rollapply(rho,FUN=sum,align='right',width=6)
  rhot6=100*(-1+exp(rhot6))
  lastrho=as.numeric(100*(-1+dat2$PX_LAST[dim(dat2)[1]]/dat2$PX_LAST[1]))
  rhot6=c(rhot6,zoo(lastrho,today()+1))
  mom=rhot6/volz 
  plot(mom,col='blue',xlab='',ylab='Momentum Index',main=names(tickers)[j])
  abline(h=quantile(mom,na.rm=TRUE)[c(2,3,4)],lty='dotted')
  rmat=merge(mom,rhof3)
  exc=which(apply(is.na(merge(mom,rhof3)),1,any))
  rmat=rmat[-exc,]
  momentum_index=rmat[,1]
  forward_3mo_return=rmat[,2]
  plot(rmat[,1],rmat[,2],pch=20,col='blue',
       main=names(tickers)[j],xlab='Momentum Index',ylab='Next 3 Month Return')
  abline(v=quantile(mom,na.rm=TRUE)[c(2,3,4)],lty='dotted')
  abline(h=0,lty='dotted')
  lastmom=as.numeric(mom[length(mom)])
  abline(v=lastmom,col='red')
  model=lm(forward_3mo_return~momentum_index)
  ci.calc=c(1,lastmom)%*%confint(model,level=.99)
  new=data.frame(momentum_index=lastmom)
  ci=predict(model,newdata = new,level=.65,interval='prediction')
  ci=ci[1,c(2,3)]
  abline(model,col='green')
  points(c(lastmom,lastmom),ci,col='red',pch=19)
  print(summary(model))
}
x=blpDisconnect(conn)
```
